Results Coding

### 2023-10-25 analysis/practiceCoding_AW.Rmd
Article exclusion & ref harmonise
Added group_by(sample_id) for article exclusion reasons to easily see reasons in both samples.

Added one additional argument to harmonise a reference statement

---
title: "Results Coding"
author: "Annie Whamond"
date: "2023-08-28"
output: html_document
---
# Load processed data files
```{r}

@@

# Calculate CIs for YES 
```{r}
library(binom)

# Prominent Sample data
prominentSuccess <- 38
randomSuccess <- 23
totalSuccess <- 57

@@

# Print the confidence interval
print(ci_prominent)
print(ci_random)
print(ci_total)
```
# Look at PPC names
```{r}

table(d_journals$ppc_name)

@@

table(PPC_length$ppc_length, PPC_length$ppc_name)
```

# Look at PPC time limitations
``` {r}
PPC_time <- d_PPConly %>%
  filter(!is.na(ppc_time)) %>%
  filter(ppc_time != "NOT STATED")

table(PPC_time$ppc_time, PPC_time$ppc_name)

@@

# Create bar plot
d_journals %>%  
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
    )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "NO") %>%
  ggplot() +
geom_bar(
  mapping = aes(x=has_ppc, fill = cope),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Journal PPC Acceptance by COPE membership", x = "Accepts PPC", y = "Count")
```

>>>>

---
title: "Results Coding"
author: "Annie Whamond"
date: "2023-08-28"
output: html_document
---

# Load libraries

```{r}
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(kableExtra) # for tables
library(knitr) # for literate programming
library(janitor) # for data munging
library(tidylog) # for inline code feedback
library(here) # for finding files
library(validate) # for data validation and testing
#library(ggthemr) # for ggplot theme
library(ggrepel) # for ggplot text labels
library(scales) # to wrap text on axis labels
library(ggdist) # for plotting distributions
library(patchwork) # for multipanel plot layouts
library(ggbeeswarm) # for dotplots
```

# Load processed data files
```{r}

@@

``` {r}

d_journalsEmp <- d_journals %>%
  filter(is_empirical == "TRUE") %>%
  filter(ppc_type == "A")

table(d_journalsEmp$field, d_journalsEmp$sample_id)

# Create tibbles for prominent and random journal samples
```{r}
dj_prom <- d_journalsEmp %>%
  mutate(sample_id = case_when(
    sample_id == "both" ~ "prominent",
    TRUE ~ sample_id
  )) %>%
  filter(sample_id == "prominent")

dj_random <- d_journalsEmp %>%
  mutate(sample_id = case_when(
    sample_id == "both" ~ "random",
    TRUE ~ sample_id
  )) %>%
  filter(sample_id == "random")
```

# Descriptives for each journal sample 
```{r}
table(dj_prom$field, dj_prom$has_ppc)
table(dj_random$field, dj_random$has_ppc)

table(dj_prom$field, dj_prom$cope)
table(dj_random$field, dj_random$cope)
```

# Plot sample id by field
```{r}

d_journals %>%
  ggplot() +
  geom_bar(
    mapping = aes(x = field, fill = sample_id),
    stat = "count",
    position = "stack",
    colour = "black",
    just = 0.5,
    width = 0.7,
    na.rm = FALSE,
    orientation = NA,
    show.legend = TRUE,
    inherit.aes = TRUE
  ) +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(title = "Sample ID by Field", x = "Field", y = "Count")

# CHAT GPT TEST
```{r}
library(dplyr)
library(ggplot2)

d_journals %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
  )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc %in% c("YES", "NO")) %>%
  filter(sample_id == 'both' | sample_id == 'random') %>%
  group_by(field, has_ppc) %>%  # Group by field and has_ppc
  summarise(count = n()) %>%   # Calculate counts for each combination
  group_by(field) %>%           # Group by field only
  mutate(percentage = round(count / sum(count) * 100)) %>%  # Calculate percentages within each field and round
  ggplot() +
  geom_bar(
    mapping = aes(x = field, y = count, fill = has_ppc),
    stat = "identity",  # Use "identity" for y values
    position = "stack",
    colour = "black",
    width = 0.7,
    na.rm = FALSE,
    orientation = NA,
    show.legend = TRUE,
    inherit.aes = TRUE
  ) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Random Journal PPC Acceptance by Field", x = "Field", y = "Count")

# Create bar plot of PPC policy by Field
```{r}

# Creates bar graph for Prominent journals

d_journals %>%  
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
    )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "NO") %>%
  filter(sample_id == 'both' | sample_id == 'prominent') %>%
  ggplot() +
geom_bar(
  mapping = aes(x=field, fill = has_ppc),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Prominent Journal PPC Acceptance by Field", x = "Field", y = "Count")
```

# Creates bar graph for Random journals
``` {r}
d_journals %>%  
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
    )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "NO") %>%
  filter(sample_id == 'both' | sample_id == 'random') %>%
  ggplot() +
geom_bar(
  mapping = aes(x=field, fill = has_ppc),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Random Journal PPC Acceptance by Field", x = "Field", y = "Count")
```

# Plot PPC length limits by Field and COPE
```{r}
d_length <- d_journals %>%
  select(has_ppc, journal_name, jif, cope, ppc_length, ppc_time, ppc_ref, field) %>%
  filter(has_ppc=="YES") %>%
  filter(ppc_length !="NOT STATED") %>%
  filter(ppc_length !="Qualitative limit")

d_length$ppc_length <- as.numeric(d_length$ppc_length)

d_length %>%
ggplot() +
  geom_point(aes(x = ppc_length, 
                               y = jif,
                              shape = cope, 
                              colour = field,
                              size=1, 
                              alpha = 0.7, 
                              show.legend = FALSE,
                              inherit.aes = FALSE)) +
  theme_grey() +
  labs(title = "Word Limits by JIF where PPC Accepted", x = "Word Limits", y = "Journal Impact Factor") +
  scale_fill_brewer(palette="Accent") 
```

# Calculate CIs for YES 
Not sure if this makes sense to do for Prominent and Total, as these are not random samples
```{r}
library(binom)

# Prominent Sample data
prominentSuccess <- 1
randomSuccess <- 23
totalSuccess <- 57

@@

# Print the confidence interval
print(ci_prominent)
print(ci_random)
print(ci_total)
```

# Calculate CIs for NO 
```{r}
library(binom)

# Prominent Sample data
prominentNO <- 77
randomNO <- 74
totalNO <- 123

# Calculate the Wilson confidence interval
ci_prominentNO <- binom.confint(prominentNO, sample_size, method = "wilson", conf.level = confidence_level)
ci_randomNO <- binom.confint(randomNO, sample_size, method = "wilson", conf.level = confidence_level)
ci_totalNO <- binom.confint(totalNO, totalSample, method = "wilson", conf.level = confidence_level)

# Print the confidence interval
print(ci_prominentNO)
print(ci_randomNO)
print(ci_totalNO)
```

# Look at PPC names
```{r}

table(d_journals$ppc_name)  #PPCnames
table(d_journals$sample_id, d_journals$ppc_name) #lists journals with PPC types

```
Total = 63, 5 journals offering 2 types

@@

dj_prominent <- d_journals %>%
  filter(sample_id != "random")

dj_random <- d_journals %>%
  filter(sample_id != "prominent")

#table_length <- table(PPC_length$ppc_length, PPC_length$ppc_name)
table(dj_prominent$ppc_length, dj_prominent$ppc_name)
table(dj_random$ppc_length, dj_random$ppc_name)
```

# Mean JIF by field and sample
```{r}

dj_prom %>%
  filter(ppc_type == "A") %>%
  group_by(field) %>%
  summarise(mnJIF = mean(jif)) %>%
  ungroup()

dj_prom %>%
  filter(ppc_type == "A") %>%
  mutate(jif = round(jif, 2)) %>%
  summarise(mean(jif), median(jif))

```{r}
dj_random %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  group_by(field) %>%
  summarise(mnJIF = mean(jif)) %>%
  ungroup()

dj_random %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  mutate(jif = round(jif, 2)) %>%
  summarise(mean(jif), median(jif))
```
# PPC and COPE
```{r}

table(dj_prom$has_ppc, dj_prom$cope)

dj_rand <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(is_empirical == TRUE)

table(dj_rand$has_ppc, dj_rand$cope)

# Look at PPC time limitations
``` {r}

table(dj_prominent$ppc_time, dj_prominent$ppc_name)
table(dj_random$ppc_time, dj_random$ppc_name)

```
CREATE FIGURES FOR TYPES OF RESTRICTION STATEMENTS

# FIGURE of PROMINENT length limits
```{r}

dj_prominent %>%
  filter(!is.na(ppc_length)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ "Quantitative",
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_length)
  )) %>%
  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Prominent_length.png", plot = last_plot(), device = "png")
```
# FIGURE of PROMINENT time limits
```{r}

dj_prominent %>%
  filter(!is.na(ppc_time)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ "Quantitative",
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_time)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_time, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "Time-to-Submit Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Prominent_time.png", plot = last_plot(), device = "png")
```
# FIGURE of PROMINENT reference limits
```{r}

dj_prominent %>%
  filter(!is.na(ppc_ref)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_ref = case_when(
    ppc_ref %in% c(10, 15, 20, 5, "max 20") ~ "Quantitative",
    ppc_ref == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_ref)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_ref, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "Reference Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Prominent_ref.png", plot = last_plot(), device = "png")
```
# FIGURE of PROMINENT Peer-Review 
```{r}

dj_prominent %>%
  filter(!is.na(ppc_review)) %>%
  filter(has_ppc != "ARCHIVE") %>%
 mutate(ppc_review = fct_relevel(
    case_when(
      ppc_review == "YES" ~ "Yes",
      ppc_review == "NO" ~ "No",
      ppc_review == "NOT STATED" ~ "Not Stated",
      TRUE ~ as.character(ppc_review)  # Keep other values as they are
    ),
    c("Not Stated", "No", "Yes")  # Specify the desired order
  )) %>%
  ggplot(mapping = aes(x = ppc_review, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "PPC Sent for Peer-review", y = "Count", fill = "PPC Type")

ggsave(filename = "Prominent_review.png", plot = last_plot(), device = "png")
```

# FIGURE of RANDOM Length Limits
```{r}

dj_random %>%
  filter(!is.na(ppc_length)) %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 2000, 2500, 2650, 500) ~ "Quantitative",
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_length)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 25)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.7)) +
  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Random_length.png", plot = last_plot(), device = "png")
```

# FIGURE of RANDOM time limits
```{r}

dj_random %>%
  filter(!is.na(ppc_time)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% 39.15 ~ "Quantitative",
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_time)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_time, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 25)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.7)) +
  labs(x = "Time-to-Submit Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Random_time.png", plot = last_plot(), device = "png")
```
# FIGURE of PROMINENT reference limits
```{r}

dj_random %>%
  filter(!is.na(ppc_ref)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_ref = case_when(
    ppc_ref %in% c(10, 15, 5) ~ "Quantitative",
    ppc_ref == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_ref)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_ref, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 25)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.7)) +
  labs(x = "Reference Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Random_ref.png", plot = last_plot(), device = "png")
```
# FIGURE of RANDOM Peer-Review 
```{r}

dj_random %>%
  filter(!is.na(ppc_review)) %>%
  filter(has_ppc != "ARCHIVE") %>%
 mutate(ppc_review = fct_relevel(
    case_when(
      ppc_review == "YES" ~ "Yes",
      ppc_review == "NO" ~ "No",
      ppc_review == "NOT STATED" ~ "Not Stated",
      TRUE ~ as.character(ppc_review)  # Keep other values as they are
    ),
    c("Not Stated", "No", "Yes")  # Specify the desired order
  )) %>%
  ggplot(mapping = aes(x = ppc_review, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 25)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.7)) +
  labs(x = "PPC Sent for Peer-review", y = "Count", fill = "PPC Type")

ggsave(filename = "Random_review.png", plot = last_plot(), device = "png")
```

# PPC Reference limits
```{r}
table(dj_prominent$ppc_ref, dj_prominent$ppc_name)
table(dj_random$ppc_ref, dj_random$ppc_name)

```
# PPC Peer Review
```{r}
table(dj_prominent$ppc_review, dj_prominent$ppc_name)
table(dj_random$ppc_review, dj_random$ppc_name)

@@

# Overall
d_journals %>%  
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
    )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "NO") %>%
  ggplot() +
geom_bar(
  mapping = aes(x=has_ppc, fill = cope),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Journal PPC Acceptance by COPE membership", x = "Accepts PPC", y = "Count")

``` {r}
# Prominent Sample
d_journals %>%  
  filter(sample_id == "prominent" | sample_id == "both") %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'NO',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
    )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "NO") %>%
  ggplot() +
geom_bar(
  mapping = aes(x=has_ppc, fill = cope),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(title = "Prominent Journal PPC Acceptance by COPE membership", x = "Accepts PPC", y = "Count", fill = "COPE")

ggsave(filename= "ProminentPPC_policyByCope.png", device= "png")
```

``` {r}
# Random Sample
d_journals %>%  
  filter(sample_id == "random" | sample_id == "both") %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
    )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "NO") %>%
  ggplot() +
geom_bar(
  mapping = aes(x=cope, fill = has_ppc),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(title = "Random Journal PPC Acceptance by COPE membership", x = "COPE Member", y = "Count", fill = "PPC")

ggsave(filename= "RandomPPC_policyByCope.png", device= "png")
```

# Presentation Graph of PPC by Sample

```{r}

library(dplyr)
library(ggplot2)
library(forcats)

library(dplyr)

# Duplicate rows with sample_id "both" and rename the duplicates as "Prominent"
duplicated_prominent_rows <- d_journals %>%
    mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
  )) %>%
  filter(ppc_type == "A") %>%
  filter(is_empirical == TRUE) %>%
  filter(sample_id == "both") %>%
  mutate(sample_id = "prominent")

# Combine the duplicated "Prominent" rows with the original data
d_journals_processed <- bind_rows(d_journals, duplicated_prominent_rows) %>%
  mutate(sample_id = recode(sample_id, "prominent" = "Prominent", "random" = "Random"))

# Now, the dataset contains the original "both" rows and their duplicates as "Prominent"

d_journals_processed %>%
   mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
  )) %>%
  filter(ppc_type == "A") %>%
  filter(is_empirical == TRUE) %>%
  mutate(sample_id = ifelse(sample_id == "both", "Random", sample_id)) %>%
  ggplot() +
  geom_bar(
    mapping = aes(x = has_ppc, fill = sample_id),
    stat = "count",
    position = position_dodge(width = 0.8),  # Use position = "dodge" to create side-by-side bars
    colour = "black",
    alpha = 0.7,
    width = 0.7,
    na.rm = FALSE,
    orientation = "vertical",
    show.legend = TRUE,
    inherit.aes = TRUE
  ) +
  geom_text(
    aes(x = has_ppc, y = ..count.., label = ..count.., group = sample_id),
    stat = "count",
    position = position_dodge(width = 0.8),
    vjust = -0.5,  # Adjust the vertical position of the labels
    size = 6
  ) +
  theme_bw() +
  ylim(0, 100) +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Journal PPC Acceptance by Sample",
       x = "Accepts PPC",
       y = "Count",
       fill = "Sample"  # Customize the legend title here
  ) + 
  theme(
    text = element_text(size = 18)  # Increase the font size here
  )

ggsave(filename = "PPCbySample.png", plot = last_plot(), device = "png")
```

# Articles and Prevalence

# Calculate CIs for NO 
```{r}
library(binom)

# Prominent Sample data for linked
plPPCsuccess <- 1
rlPPCsuccess <- 0
linkedSample <- 101

confidence_level <- 0.95

# Calculate the Wilson confidence interval
ci_plPPC <- binom.confint(plPPCsuccess, linkedSample, method = "wilson", conf.level = confidence_level)
ci_rlPPC <- binom.confint(rlPPCsuccess, linkedSample, method = "wilson", conf.level = confidence_level)

# Print the confidence interval
print(ci_plPPC)
print(ci_rlPPC)

```
```{r}
library(dplyr)
library(ggplot2)
library(forcats)

# Modify the dataset to ensure "both" values are included in both "Prominent" and "Random"
d_journals_processed <- d_journals %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
  )) %>%
  filter(ppc_type == "A") %>%
  filter(is_empirical == TRUE) %>%
  mutate(sample_id = fct_recode(sample_id, 
                                "Prominent" = "prominent", 
                                "Random" = "random",
                                "Both" = "both"))

# Create a summary dataset to count "both" values in both "Prominent" and "Random"
summary_data <- d_journals_processed %>%
  filter(sample_id %in% c("Prominent", "Random")) %>%
  group_by(has_ppc, sample_id) %>%
  summarise(count = sum(count)) %>%
  ungroup()

# Create the ggplot with count labels
ggplot(data = summary_data) +
  geom_bar(
    mapping = aes(x = has_ppc, y = count, fill = sample_id),
    stat = "identity",  # Use stat = "identity" to specify y as the count values
    position = position_dodge(width = 0.8),
    colour = "black",
    alpha = 0.7,
    width = 0.7,
    na.rm = FALSE,
    orientation = "vertical",
    show.legend = TRUE,
    inherit.aes = TRUE
  ) +
  geom_text(
    aes(x = has_ppc, y = count, label = count, group = sample_id),
    position = position_dodge(width = 0.8),
    vjust = -0.5,
    size = 4
  ) +
  theme_bw() +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Journal PPC Acceptance by Sample",
       x = "Accepts PPC",
       y = "Count",
       fill = "Sample Type"
  ) + 
  theme(
    text = element_text(size = 18)
  )

# Save the plot
ggsave(filename = "PPCbySample.png", plot = last_plot(), device = "png")

```
# Restriction Statements Graph
```{r}

table(dj_prominent$ppc_ref)
table(dj_prominent$ppc_review)

table(dj_random$ppc_ref)
table(dj_random$ppc_review)
```

# Check median and IQR for each field
```{r}

# Group the tibble by the 'field' column
prom_grouped <- dj_prom %>% group_by(field)

# Compute summary statistics for 'jif' within each group
promJIF_stats <- prom_grouped %>%
  mutate(jif = round(jif, 2)) %>%
  summarize(
    mean_jif = mean(jif),
    median_jif = median(jif),
    q1_jif = quantile(jif, 0.25),
    q3_jif = quantile(jif, 0.75),
    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
    count = n()
  )

# View the summary statistics
print(promJIF_stats)
```

#For randomly sampled journals 
``` {r}
# Group the tibble by the 'field' column
rand_grouped <- dj_rand %>% filter(!is.na(jif)) %>% group_by(field)

# Compute summary statistics for 'jif' within each group
randJIF_stats <- rand_grouped %>%
  filter(ppc_type == "A") %>%
  filter(is_empirical == "TRUE") %>%
  mutate(jif = round(jif, 2)) %>%
  summarize(
    mean_jif = mean(jif),
    median_jif = median(jif),
    q1_jif = quantile(jif, 0.25),
    q3_jif = quantile(jif, 0.75),
    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
    count = n()
  )

# View the summary statistics
print(randJIF_stats)

dj_rand %>%
   filter(!is.na(jif)) %>%
  mutate(jif = round(jif, 2)) %>%
  summarize(
    mean_jif = mean(jif),
    median_jif = median(jif),
    q1_jif = quantile(jif, 0.25),
    q3_jif = quantile(jif, 0.75),
    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
    count = n()
  )

```
```{r}
count_non_missing <- sum(!is.na(dj_prominent$ppc_length))
cat("Count of non-missing values in ppc_length:", count_non_missing, "\n")
```

# View median and IQR for quantitavtive 'Commentary' limits in prominent journals
```{r}

promCom_stats <- dj_prominent %>%
  filter(ppc_name == "Commentary") %>%
  mutate(
    ppc_length = as.numeric(replace(ppc_length, ppc_length %in% c("Qualitative", "NOT STATED"), NA)),
    ppc_time = as.numeric(replace(ppc_time, ppc_time %in% c("Qualitative", "NOT STATED"), NA)),
    ppc_ref = as.numeric(replace(ppc_ref, ppc_ref %in% c("Qualitative", "NOT STATED"), NA))
  ) %>%
  summarize(
    mdLength = median(ppc_length, na.rm = TRUE),
    mdTime = median(ppc_time, na.rm = TRUE),
    mdRef = median(ppc_ref, na.rm = TRUE),
    q1_length = quantile(ppc_length, 0.25, na.rm = TRUE),
    q3_length = quantile(ppc_length, 0.75, na.rm = TRUE),
    iqr_length = quantile(ppc_length, 0.75, na.rm = TRUE) - quantile(ppc_length, 0.25, na.rm = TRUE),
    q1_time = quantile(ppc_time, 0.25, na.rm = TRUE),
    q3_time = quantile(ppc_time, 0.75, na.rm = TRUE),
    iqr_time = quantile(ppc_time, 0.75, na.rm = TRUE) - quantile(ppc_time, 0.25, na.rm = TRUE),
    q1_ref = quantile(ppc_ref, 0.25, na.rm = TRUE),
    q3_ref = quantile(ppc_ref, 0.75, na.rm = TRUE),
    iqr_ref = quantile(ppc_ref, 0.75, na.rm = TRUE) - quantile(ppc_ref, 0.25, na.rm = TRUE),
    peer_rev = sum(ppc_review == "YES"),
    COPE = sum(cope == "TRUE")
  )

print(promCom_stats)

```
# View median and IQR for quantitavtive 'Letters' limits in prominent journals
```{r}
promLet_stats <- dj_prominent %>%
  filter(ppc_name == "Letters") %>%
  mutate(
    ppc_length = as.numeric(ppc_length),  # Convert ppc_length to numeric
    ppc_time = as.numeric(ppc_time),      # Convert ppc_time to numeric
    ppc_ref = as.numeric(ppc_ref)         # Convert ppc_ref to numeric
  ) %>%
  summarize(
    mdLength = median(ppc_length, na.rm = TRUE),
    mdTime = median(ppc_time, na.rm = TRUE),
    mdRef = median(ppc_ref, na.rm = TRUE),
    q1_length = quantile(ppc_length, 0.25, na.rm = TRUE),
    q3_length = quantile(ppc_length, 0.75, na.rm = TRUE),
    iqr_length = quantile(ppc_length, 0.75, na.rm = TRUE) - quantile(ppc_length, 0.25, na.rm = TRUE),
    q1_time = quantile(ppc_time, 0.25, na.rm = TRUE),
    q3_time = quantile(ppc_time, 0.75, na.rm = TRUE),
    iqr_time = quantile(ppc_time, 0.75, na.rm = TRUE) - quantile(ppc_time, 0.25, na.rm = TRUE),
    q1_ref = quantile(ppc_ref, 0.25, na.rm = TRUE),
    q3_ref = quantile(ppc_ref, 0.75, na.rm = TRUE),
    iqr_ref = quantile(ppc_ref, 0.75, na.rm = TRUE) - quantile(ppc_ref, 0.25, na.rm = TRUE),
    peer_rev = sum(ppc_review == "YES"),
    COPE = sum(cope == "TRUE")
  )

print(promLet_stats)
```
# View median and IQR for ALL quantitavtive limits in PROMINENT journals
```{r}

promAll_stats <- dj_prominent %>%
  filter(ppc_name == "Commentary" | ppc_name == "Letters") %>%
  mutate(
    ppc_length = as.numeric(replace(ppc_length, ppc_length %in% c("Qualitative", "NOT STATED"), NA)),
    ppc_time = as.numeric(replace(ppc_time, ppc_time %in% c("Qualitative", "NOT STATED"), NA)),
    ppc_ref = as.numeric(replace(ppc_ref, ppc_ref %in% c("Qualitative", "NOT STATED"), NA))
  ) %>%
  summarize(
    mdLength = median(ppc_length, na.rm = TRUE),
    mdTime = median(ppc_time, na.rm = TRUE),
    mdRef = median(ppc_ref, na.rm = TRUE),
    q1_length = quantile(ppc_length, 0.25, na.rm = TRUE),
    q3_length = quantile(ppc_length, 0.75, na.rm = TRUE),
    iqr_length = quantile(ppc_length, 0.75, na.rm = TRUE) - quantile(ppc_length, 0.25, na.rm = TRUE),
    q1_time = quantile(ppc_time, 0.25, na.rm = TRUE),
    q3_time = quantile(ppc_time, 0.75, na.rm = TRUE),
    iqr_time = quantile(ppc_time, 0.75, na.rm = TRUE) - quantile(ppc_time, 0.25, na.rm = TRUE),
    q1_ref = quantile(ppc_ref, 0.25, na.rm = TRUE),
    q3_ref = quantile(ppc_ref, 0.75, na.rm = TRUE),
    iqr_ref = quantile(ppc_ref, 0.75, na.rm = TRUE) - quantile(ppc_ref, 0.25, na.rm = TRUE),
    peer_rev = sum(ppc_review == "YES"),
    COPE = sum(cope == "TRUE"),
    count = n()
  )

print(promAll_stats)

# View median and IQR for quantitavtive 'Commentary' limits in Random journals
```{r}
